Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-05-25 paper/methodology.tex
more edits to the methodology section to comply with journal guidelines

\begin{figure}[h]
	\centering
	Placeholder % TODO: \includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
	\caption{Schematic of QASS algorithm}
	\label{fig:qassplan}
\end{figure}

@@

Adaptive sampling techniques appear frequently in the literature and have been
specialised for surrogate modelling. Garud's~\cite{Garud2016} ``Smart Sampling
Algorithm'' achieved notable success by incorporating surrogate quality and
crowding distance scoring to identify optimal new samples, but was only tested
on a single-parameter domain. We theorised that a nondeterministic sample
generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
fare better for high-dimensional models by more thoroughly exploring all local
optima in the feature space. MCMC produces a progressive chain of sample points,
each drawn according to the same symmetric proposal distribution\footnote{An
adaptive MCMC procedure~\cite{Zhang2012}, which adjusts an ellipsoidal proposal
distribution to fit the posterior, was also implemented but not fully tested.}
from the prior point. These sample points will converge to a desired posterior
distribution, so long as the acceptance probability for these draws has a
particular functional dependence on that posterior value (see~\cite{Zhou2018}
for a review).

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS,
Figure~\ref{fig:qassplan}) to iteratively increment the training/test set with sample
points which maximise surrogate error and minimise a crowding distance metric
(CDM)~\cite{Solonen2012} in feature space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
	\caption{Schematic of QASS algorithm}
	\label{fig:qassplan}
\end{figure}

@@

Adaptive sampling techniques appear frequently in the literature and have been
specialised for surrogate modelling. Garud's~\cite{Garud2016} ``Smart Sampling
Algorithm'' achieved notable success by incorporating surrogate quality and
crowding distance scoring to identify optimal new samples, but was only tested
on a single-parameter domain. We theorised that a nondeterministic sample
generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
fare better for high-dimensional models by more thoroughly exploring all local
optima in the feature space. MCMC produces a progressive chain of sample points,
each drawn according to the same symmetric proposal
distribution\todo{Incorporate the footnote into the text.}\footnote{An
adaptive MCMC procedure~\cite{Zhang2012}, which adjusts an ellipsoidal proposal
distribution to fit the posterior, was also implemented but not fully tested.}
from the prior point. These sample points will converge to a desired posterior
distribution, so long as the acceptance probability for these draws has a
particular functional dependence on that posterior value (see~\cite{Zhou2018}
for a review).

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \fref{fig:qassplan}) to iteratively increment the training/test set with sample
points which maximise surrogate error and minimise a crowding distance metric
(CDM)~\cite{Solonen2012} in feature space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.
